---
title: "Data Preparation - European and World Values Survey"
---

## Preparation

directories
```{r}
# data_dir = "/path/to/data/directory/"
# out_dir = "/path/to/output/directory/"
data_dir = "/Users/sjifradeleeuw/surfdrive/University\ of\ Amsterdam/Study\ 1/Data/"
out_dir = "/Users/sjifradeleeuw/GitHub/"
```

import stata pooled EVS-WVS dataset and subset relevant variables: 
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
df = haven::read_dta(paste0(data_dir, "name_wvs_evs_pooled.dta"))

df = subset(df, select = c(
 "S003", "S003A", 
 "E114", "E116", "E117", "E120", "E121", "E122", "E123", 
 "E033", "X002", "S020", "X001", "X025", "A006", "X002_02", "E023",
 "G033", "G034", "G035", "G036", "G037",
 "E043", "E044", "E037",
 "E035",
 "Y023B", "Y023C", "Y023A",
 "Y022A", "Y022B", "Y022C"
 ))

colnames(df) = c(
 "country", "country_split", 
 "dap_strongleader", "dap_army", "dap_dem", "dap_economy", "dap_indecisive", "dap_order", "dap_better", 
 "lrscale", "birth", "year", "gndr", "educ", "relig", "native", "polint",
 "nat1", "nat2", "nat3", "nat4", "nat5",
 "socpol1", "socpol2", "socpol3",
 "inceq",
 "lib1", "lib2", "lib3",
 "equality1", "equality2", "equality3"
 )
```

Obtain variable label, labels and description and save in file:
```{r}
varlist = list()
labels = list()
varnames = names(df)

for (i in c(2:length(df))) {
 varname = names(df[,i]); var = df[,varname]; colnames(var) = c("var")
 j = i-1
 name = varnames[i]
 if (is.null(attributes(var$var)) == TRUE) {
  label = "NA"
  values = "NA"
 } else {
  label = attributes(var$var)[1]
  values = as.character(attributes(var$var)[2])
 }
 row = data.frame(name = name, label = label, values = values)
 colnames(row) = c("name", "label", "values")
 varlist[[j]] = row
}

varlist = do.call(rbind, varlist)
varlist$values = as.character(varlist$values)
varlist$values = stringr::str_remove(varlist$values, "c\\(")
varlist$values = stringr::str_remove(varlist$values, "\\)")
write.csv(varlist, paste0(out_dir, "wvs-variablelist.csv"))
```

`function` to assign `NA` to missings and take rowmean:
```{r}
rowmean_miss = function(variables_vec, misvalues_vec) {
 data = subset(df, select = variables_vec)
 
 miss = function(x) { 
  for (i in c(1:length(misvalues_vec))) {
  value = misvalues_vec[i]; x[x == value] = NA}
  return(x)}
  
 data = data.frame(lapply(data, FUN = miss))
 data = rowMeans(data, na.rm = TRUE)
 return(data)
}
```

Correlational variables
```{r}
df$nat = 4 - rowmean_miss(c("nat1", "nat2", "nat3", "nat4", "nat5"), c(-4)) # nationalism
df$socpol = rowmean_miss(c("socpol1", "socpol2", "socpol3"), c(-5:0)) # social policies
df$inceq = rowmean_miss(c("inceq"), c(-5:0)) # income inequality 
df$lib =  rowmean_miss(c("lib1", "lib2", "lib3"), c(NA)) # liberalism
df$equality = rowmean_miss(c("equality1", "equality2", "equality3"), c(-5:0)) # gender equality
```

Demographic controls 
```{r}
df$sex = factor(df$gndr, levels = c(1,2), labels = c("Male", "Female")) 
df$educ = factor(df$educ, levels = c(1:8), 
                    labels = c("Uncompleted Primary", "Completed Primary", 
                               "Uncompleted Secondary Vocational", "Completed Secondary Vocational",
                               "Uncompleted Secondary Academic", "Completed Secondary Academic", 
                               "University without Official Degree", "University with Official Degree"))
df$relig = as.numeric(df$relig) 
df$polint[df$polint <= 0] = NA; df$polint = as.numeric(df$polint) 
df$native[df$native <0] = NA 
```

## Dependent Variable 

**positive end**: recode so that higher values indicate more support for democracy

1. (-) `dap_better`: 1 agree strongly - 4 disagree strongly
2. (-) `dap_dem`: 1 very good - 4 very bad

**negative end**: recode so that higher values indicate more support for autocracy

1. (-) `dap_leader`: 1 very good - 4 very bad
2. (-) `dap_army`: 1 very good - 4 very bad
3. (-) `dap_economy`: 1 agree strongly - 4 disagree strongly
4. (-) `dap_indecisive`: 1 agree strongly - 4 disagree strongly
5. (-) `dap_order`: 1 agree strongly - 4 disagree strongly

`function` to invert variable:
```{r}
inv = function(x) {
 x = x - min(x, na.rm = TRUE)
 x = max(x, na.rm = TRUE) - x
 return(x)
}
```

```{r}
df$autdem = 
 rowMeans(cbind(inv(df$dap_dem), inv(df$dap_better)), na.rm = TRUE) - 
 rowMeans(cbind(inv(df$dap_strongleader), inv(df$dap_army), inv(df$dap_economy), 
                inv(df$dap_indecisive), inv(df$dap_order)), na.rm = TRUE)

hist(df$autdem, main = "Distribution Democracy-Autocracy Index",
     xlab = "Value", ylab = "Frequency",  col = "gray")
```

## Country-Level Variables

## Independent Variables

First hand experiences with authoritarianism 
```{r}
df$age_5 = df$birth + 5 # variable for year at which individual turned 5
df$exp = 0
df$exp[df$age_5 <= df$endyear] = 1 # dummy indicating experience with authoritarianism
```

2. Years of Exposure

```{r}
df$duration = df$endyear - df$startyear
df$exposure = NA
df$exposure = df$endyear - df$age_5
df$exposure[df$exposure < 0] = 0
df$diff =  df$duration - df$exposure
df$diff[df$diff >= 0] = 0 
df$exposure = df$exposure + df$diff
df$exposure[df$legacy=="Democratic"] = 0
```

3. Age of Exposure 

```{r}
df$age_18 = df$birth + 18 
df$exposure_age[df$age_18 <= df$startyear] = 2 # Adult Exposure 
df$exposure_age[df$age_18 >= df$startyear] = 3 # Full Exposure
df$exposure_age[df$age_18 >= df$endyear] = 4 # Early Exposure 
df$exposure_age[df$exposure == 0] = 1 # No Exposure 
```

4. General Age

```{r}
df$age = df$year - df$birth
```

5. Period

```{r}
df$wave = NA
df$wave[df$survey == "wvs1994"] = 1 
df$wave[df$survey == "evs1999"] = 2
df$wave[df$survey == "wvs1999"] = 3 
df$wave[df$survey == "evs2008"] = 4 
```


## Save Data

```{r}
save = subset(df, select = c(
  "cntry", 
  "autdem", 
  "lrscale",
  "legacy",
  "age",
  "exp",
  "exposure",
  "exposure_age",
  "survey",
  "gndr",
  "educ",
  "relig",
  "wave"
  ))
```


```{r}
write_xlsx(save, path = "/Users/sjifradeleeuw/Dropbox/PhD/Study 1/final.xlsx", col_names = TRUE)
```






