---
title: "Data Preparation - Varieties of Democracy Data"
---

Disclaimer: the index for indoctrination was borrowed from Dinas & Northmore-Ball (2019). The validation of this measure can be found in the supplementary material of their study: https://journals.sagepub.com/doi/abs/10.1177/0010414019852699?journalCode=cpsas

```{r}
data_dir = "/path/to/directory"  # edit 
```

Import data and change directory
```{r}
vdem = haven::read_dta(paste0(data_dir, "vdem.dta")) 
vdem$country_name[vdem$country_name == "Germany"] = "West Germany"
vdem$cntry = vdem$country_name
```

# Variables

## Indoctrination

**monopolization of political discourse:** the ability to prevent alternative political discourse)

- `v2cldiscm` `v2cldiscw`: Freedom of discussion for men and women 0-4
- `v2mecenefm`: Government censorship effort 0-4
- `v2meharjrn`: harassment of journalists 0-4
- `v2meslfcen`: media self-censorship 0-3
- `v2clacfree`: freedom of academic and cultural expression 0-4
- `v2mebias`: Media bias
- `v2mecrit`: Print/broadcast media critical
- `v2merange`: Print/broadcast media perspectives

**Presence of clear ideology*/message**

- `v2dlreason`: Reasoned justification REVERSE 0-3

**Control and exclusion** of political parties and opposition groups and civil society.

- `v2psparban`: Party ban (C) 0-4 ; 0: Yes. All parties except the state-sponsored party are banned. 
- `v2cseeorgs`: CSO entry and exit (C) 0-4  Government control over civil society organizations
- `v2csprtcpt`: CSO participatory environment (C) 0-3  Zero value best captures regimes that are good at indoctrination: 

**Capacity for mass moblization** through mass membership organizations such as parties

- `v2psorgs`: Party organizations: 0-4 REVERSE Question: Permanent organizations for political parties. No - 4: All.
- `v2psprbrch`: Party branches: 0-4 REVERSE How many parties have local branches? 0: None --> 4: All

**Mass education sytem**
- `v2peedueq`: Educational equality 0-4 REVERSE scale (multiply by -1)

Index:
```{r}
# reverse items
vdem$v2peedueq_rev=vdem$v2peedueq*-1 
vdem$v2psprbrch_rev=vdem$v2psprbrch*-1 
vdem$v2psorgs_rev=vdem$v2psorgs*-1  
vdem$v2dlreason_rev= vdem$v2dlreason*-1 

# row mean for each sub-index
vdem$monopolization = rowMeans(subset(vdem, select = 
   c("v2cldiscm", "v2cldiscw", "v2mecenefm", "v2meharjrn", "v2meslfcen", 
     "v2clacfree","v2mebias", "v2mecrit", "v2merange" )), na.rm = TRUE)
vdem$ideology = vdem$v2dlreason_rev
vdem$control = rowMeans(subset(vdem, select = c("v2psparban", "v2cseeorgs", "v2csprtcpt")))
vdem$mobilization = rowMeans(subset(vdem, select = c("v2psorgs_rev", "v2psprbrch_rev")))
vdem$education = vdem$v2peedueq_rev

# collapse into single index 
vdem$indoctrination = rowMeans(subset(vdem, select = c("monopolization", "ideology", "control", "mobilization", "education")))
```

## Repression 

Civil liberty index to measure regime repression.
```{r}
vdem$repression = vdem$v2x_civlib
```

# Imputation

Missing values are introduced when countries were formerly part of other countries. We impute the missing data with that of the country they historically belonged to. 

`function` to impute the missing values of `country1` by those of `country2` for one particular variable.
```{r}
impute = function(country1, country2, variable) {
 vdem = subset(vdem, select = c("country_name", "year", variable))
 data1 = subset(vdem, country_name == country1); data2 = subset(vdem, country_name == country2)
 data = merge(data1, data2, by = c("year"), all = TRUE)
 variable_x = paste0(variable, ".x"); variable_y = paste0(variable, ".y")
 newvariable = data[,variable_x]; newvariable[is.na(newvariable)] = data[,variable_y]
 data = data.frame(country = country1, year = data$year, variable = newvariable)
 return(data)
}
```

`function` to replace 
```{r}
combine = function(list, variable, name) {
 newdata = do.call(rbind, list)
 olddata = subset(vdem, select = c("country_name", "year", variable))
 colnames(olddata) = c("country", "year", "variable")
 olddata = subset(olddata, country != unique(newdata$country))
 data = data.frame(rbind(newdata, olddata))
 colnames(data) = c("country", "year", name)
 data$country = as.character(data$country)
 return(data)
}
```

Impute missing values and append to original dataset.s
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
# list of countries for which the missing values are to be imputed. 
# Each vector in the list contains c(country1, country2) in the impute() function
replace = list(c("West Germany", "Germany"), c("German Democratic Republic", "Germany"), c("Belarus", "Russia"), 
               c("Armenia", "Russia"), c("Georgia", "Russia"), c("Macedonia", "Serbia"), c("Ukraine", "Russia"),
               c("Slovenia", "Serbia"), c("Moldova", "Russia"), c("Bosnia and Herzegovina", "Serbia"))

# empty list to store new data in
repression = list()
indoctrination = list()
elecdem = list()

# impute data for each country in replace-list and store in empty lists
for (i in c(1:length(replace))) {
 country = replace[[i]]
 repression[[i]] = impute(country[1], country[2], "v2x_civlib")
 indoctrination[[i]] = impute(country[1], country[2], "indoctrination")
 elecdem[[i]] = impute(country[1], country[2], "v2x_polyarchy")
}

# combine with original dataframe
repression = combine(repression, "v2x_civlib", "repression")
indoctrination = combine(indoctrination, "indoctrination", "indoctrination")
elecdem = combine(elecdem, "v2x_polyarchy", "elecdem")

# rename countries
vdem2 = data.frame(repression, indoctrination = indoctrination[,3], electdem = elecdem[,3])
vdem2 = subset(vdem2, year >= 1900)
vdem2$country[vdem2$country=="German Democratic Republic"] = "East Germany"
vdem2$country[vdem2$country=="Bosnia and Herzegovina"] = "Bosnia"
vdem2$country[vdem2$country=="Czech Republic"] = "Czechia"
vdem2 = merge(vdem2, agg, by = c("country"))
vdem2$id = with(vdem2, ave(rep(1, nrow(vdem2)), country, FUN = seq_along))

# save data 
write.csv(vdem2, paste0(data_dir, "vdem_subset.csv"))
```


